Paper Wireframe

### 2018-07-17 paper_wireframe_knit.Rmd
Addition of habitat and leaflet viewer

@@

## fill NA in mig route

# fills some
dat<-left_join(dat, select(extraz, ptt, year, autumn_mig), by=c('ptt', 'year'))

@@

@@

Anova(m5, test.statistic = 'F')
```

@@

## Endogenous factors that influence dpearture date from West Africa.

@@

Anova(m1, test.statistic = 'F')

@@

@@

map = map_data("world")
map = subset(map, region=='Africa')

ggplot() + geom_polygon(data = map,
               aes(x=long, y = lat, group = group),
               fill = NA, colour="darkgray", size=0.5)+
  geom_point(data=lastWASO, aes(x=long, y=lat, colour=factor(ptt)), shape=1, size=2)+
  geom_line(data=lastWASO, aes(x=long, y=lat, colour=factor(ptt)), alpha=0.2)+coord_cartesian()+
   coord_map(xlim = c(-16, 5),ylim = c(14, 3))+xlab('Longitude')+ylab('Latitude')+theme_bw()+ labs(colour = "Bird ID")
```

@@

@@

summary(m6)

@@

qplot(data=dat3, x=aquaANOM, y=DEPwestAF)+
  geom_line(data=newdat, aes(x=aquaANOM, y=p1), colour='red')+
  geom_line(data=newdat, aes(x=aquaANOM, y=lc), colour='red', linetype='dashed')+
  geom_line(data=newdat, aes(x=aquaANOM, y=uc), colour='red', linetype='dashed')+
  xlab("NDVI anomoly")+
  ylab("Departure date West Africa (DOY)")+
  theme_bw()

Anova(m6, test.statistic = 'F')

>>>>

## landcover and river data
lc<-read.csv("C:/cuckoo_tracking/data/stopover_bestofday_2018_1daymin_recalc_spring_mig_detailcoords_landcov_ext_rivers.csv", h=T)

#extra data for filling migratory route

@@

## fill NA in mig route
# fills some
dat<-left_join(dat, select(extraz, ptt, year, autumn_mig), by=c('ptt', 'year'))

@@

### Add departure info from WA e.g. country, lat and long, length of final stopover and 2nd before last

notWA<-c('Italy', 'France', 'Spain', 'Algeria',
        'United Kingdom', 'Morocco', 'Portugal')

soversWA<-sovers[-which(sovers$country %in% notWA),]

dat<-left_join(dat, soversWA %>% group_by(ptt, year) %>% summarise( dep_country=last(country), dep_long=last(SO_median_long), dep_lat=last(SO_median_lat), st_finalSO=last(SO_startDOY), dur_finalSO_n2=(nth(SO_endDOY, -2)-nth(SO_startDOY, -2))), by=c('ptt', 'year'))

#calc final stopover length (cos we corrected some values in the summary table)

dat$dur_finalSO=dat$DEPwestAF-dat$st_finalSO

#landcover metrics

lc1<-lc %>% group_by(ptt, year, SO_startDOY) %>% dplyr::summarise(Tree=mean(Trees, na.rm=T), Grass=mean(Grasslands, na.rm=T), Crops=mean(Croplands, na.rm=T), Shrub=mean(Shrubs, na.rm=T),Bare=mean(Bare.areas, na.rm=T), Urban=mean(Built.up.areas, na.rm=T),
  Aquatic=mean(Aquatic.veg.reg.flooded, na.rm=T), Water=mean(Open.water, na.rm=T), D_riv=
    mean(d_river), D_riv2=mean(d_river_str2))

# landcover types expressed as a precentage                                                            
lc1[,4:10]<-round(lc1[,4:10]/rowSums(lc1[,4:10], na.rm=T) *100)                             
# join stopover duration to test associations

lc1<-left_join(lc1, select(soversWA, ptt, year, SO_startDOY, SO_days), by=c('ptt', 'year', 'SO_startDOY'))

@@

#Anova(m5, test.statistic = 'F')
```

@@

## Endogenous factors that influence departure date from West Africa.

@@

#Anova(m1, test.statistic = 'F')

@@

```{r, warning=T, message=T, echo=F}

@@

map = map_data("world")

ggplot() + geom_polygon(data = map,
               aes(x=long, y = lat, group = group),fill = NA, colour="darkgray", size=0.5)+
  geom_point(data=lastWASO, aes(x=long, y=lat, colour=factor(ptt)), shape=1, size=2)+
  geom_line(data=lastWASO, aes(x=long, y=lat, colour=factor(ptt)), alpha=0.2)+coord_cartesian()+
   coord_map(xlim = c(-16, 5),ylim = c(14, 3))+xlab('Longitude')+ylab('Latitude')+theme_bw()+ labs(colour = "Bird ID")

@@

Country of departure seems to have little overall affect on date of departure but note that birds who leave early (< day 100) all leave from Ivory Coast and (to a lesser extent) Ghana.

#Anova(lmer(DEPwestAF~dep_country+ (1|ptt)+(1|year), data=dat), test.statistic = 'F')

dtemp<-na.omit(dat[,c(6,22:24)])

dtemp$dep_country<-factor(dtemp$dep_country, levels=c('Sierra Leone', 'Guinea', "Cote d'Ivoire", 'Ghana', 'Burkina Faso', 'Nigeria'))
m1<-lmer(DEPwestAF~breeding_loc+(1|year)+(1|ptt), data=dat)

#Anova(m1, test.statistic = 'F')

ggplot(data=dtemp, aes(x=dep_country, y=DEPwestAF ))+xlab("Departure country")+ylab("Departure date West Africa (DOY)")+geom_jitter(width=0.1,shape=1)+theme_bw()+geom_label(data=data.frame(), aes(label = 'Anova F=0.552, p=0.735', x = -Inf, y = Inf), hjust = 0, vjust = 1)+theme(axis.text.x=element_text(angle=90))
```

 Habitat?? - test each category against dep from west africa

```{r, warning=F, message=F, echo=F} 
ggplot(data=dat, aes(x=dur_finalSO, y=DEPwestAF ))+xlab("Departure country")+ylab("Departure date West Africa (DOY)")+geom_point(shape=1)+theme_bw()

Explore dataset

```{r, warning=F, message=F, echo=F} 
library(sf)
library(leaflet)

dat_sp<-st_as_sf(na.omit(dat[,c(1,2,6,23,24)]), coords = c("dep_long","dep_lat"), crs="+proj=longlat +datum=WGS84")

m <- leaflet() %>%
  addTiles() %>% 
  addMarkers(data = dat_sp, popup= paste("ptt:", dat_sp$ptt, "<br>", "year:", dat_sp$year,"<br>", "Departure date:", dat_sp$DEPwestAF))

m

@@

#summary(m6)

@@

qplot(data=dat3, x=aquaANOM, y=DEPwestAF)+
  geom_line(data=newdat, aes(x=aquaANOM, y=p1), colour='red')+
  geom_line(data=newdat, aes(x=aquaANOM, y=lc), colour='red', linetype='dashed')+
  geom_line(data=newdat, aes(x=aquaANOM, y=uc), colour='red', linetype='dashed')+
  xlab("NDVI anomoly")+
  ylab("Departure date West Africa (DOY)")+
  theme_bw()+geom_label(data=data.frame(), aes(label = 'Anova F=4.65, p=0.038', x = -Inf, y = Inf), hjust = 0, vjust = 1)+theme(axis.text.x=element_text(angle=90))

#Anova(m6, test.statistic = 'F')
